Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-11 paper/main.tex
matrix

There are two important methods to keep the passowrd safely. The first one is IAM role. IAM role provides good security protection in the whole structure.
Different IAM roles are generated to attach to different Lambda functions. The execution roles are granted permission of access to necessary AWS services. 
There are some common policies for them, e.g. AWSLambdaBasicExecutionRole and AmazonS3FullAccess policies. The second one is Secrets Manager service in AWS.
All of the passwords in this project are stored in it. Visiting it through Secrets Manager when needed.

@@

\subsection{IAM}

@@

Every role is attached the least privileges that is provided by AWS policies. As for project managers, role of A2PM is a administrator role. So it is 
attached the AdministratorAccess policy. A2DBA is attached AmazonRDSFullAccess policy, which is used by database administrator. A2Backend is attached 
AmazonRDSReadOnlyAccess and AmazonEC2ContainerServiceRole policies, which is used by backend engineers. A2Frontend is attached AmazonEC2ContainerServiceforEC2Role 
policy and A2testing is attached AmazonEC2ReadOnlyAccess policy.All the roles can protect the cloud environment and keep the least privilege. Practically, it is 
a little bit complicated for a small team, but it is useful especially when someone's credentials exposure at Github. And for the high privileges, only 
limited role can visit the sensitive resources, for example, project managers can visit almost all of the resources.

Some roles are generated for the specific service. For example, there is a role named ec2callsecretsmanager. It is attached the SecretsManagerReadWrite 
policy, which is used for a EC2 instance to visit the Secrets Manager service in AWS. It is a good method to hide the original password in the code and a 
convenient approach to get the privilege from one service to another service without any code.

\subsection{Customer data}

\subsubsection{Step 1. Identify \& Category}

\subsubsection{Step 2. High level: who can access}

\subsubsection{Step 3. Policy from cloud IAM}

\subsubsection{Step 4.what is more}

@@

The last step is to configure the security groups for step 1 and 2. In this demo, 3 zones are divided for 3 subnets, which is shown as Fig.~\ref{Security}. The inbound 
rules of zone A and B allows port 80, which is the http service port connected by ELB in front of them. The inbound of zone C allows port 8080, which is the Tomcat 
service port connected by instances in the zone A and B. And the outbound allows port 3306, which is the Mysql service port.

@@

Totally it spend 70\$. The imagery processing accounted for 50 percent. EC2 accounted 20 percent. RDS accounted 30 percent.

>>>>

There are two important methods to keep the password safely. The first one is IAM role. IAM role provides good security protection in the whole structure.
Different IAM roles are generated to attach to different Lambda functions. The execution roles are granted permission of access to necessary AWS services. 
There are some common policies for them, e.g. AWSLambdaBasicExecutionRole and AmazonS3FullAccess policies. The second one is Secrets Manager service in AWS.
All of the passwords in this project are stored in it. Visiting it through Secrets Manager when needed.

@@

\subsection{Identity and Access management}

@@

Every role is attached the least privileges which is provided by AWS policies. As for project managers, role of A2PM is a administrator role. So it is 
attached the AdministratorAccess policy. A2DBA is attached AmazonRDSFullAccess policy, which is used by database administrator. A2Backend is attached 
AmazonRDSReadOnlyAccess and AmazonEC2ContainerServiceRole policies, which is used by backend engineers. A2Frontend is attached AmazonEC2ContainerServiceforEC2Role 
policy and A2testing is attached AmazonEC2ReadOnlyAccess policy.All the roles can protect the cloud environment and keep the least privilege. Practically, it is 
a little bit complicated for a small team, but it is useful especially when someone's credentials exposure at Github. And for the high privileges, only 
limited role can visit the sensitive resources, for example, project managers can visit almost all of the resources.

Some roles are generated for the specific application. For example, there is a role named ec2callsecretsmanager. It is attached the SecretsManagerReadWrite 
policy, which is used for a EC2 instance to visit the Secrets Manager service in AWS. It is a good method to hide the original password in the code and a 
convenient approach to get the privilege from one service to another service without any code.

For users, because the demo do not allow them to visit the visualisation without login, there are two roles. One is for guests, another is for login users. 
Guests role is virtual. Guests can sign in with Gihub accounts. Github Oauth ensure the authentication securely. Once they become authenticated users, 
all the visualisation can be shown, but they only have the read permission of the visualisation.

\subsection{Data security}

Data in this demo is mainly in RDS MySQL, which is a kind of data in PaaS service model. There are two tables inclduing "main" and "users". The table "main" 
stores all of the data needed by the visualisation. The another one stores all of the user's information. There are some steps to ensure the data security.

\subsubsection{Step 1. Identification \& Category}

S3 public data are also used in this demo. Everyone can read this data, so there is no special permission setting in this demo. RDS MySQL provided the authentication 
by itself. The user and password can be used for the RDS MySQL. Moreover, the password is automatically generated and rotated by a Lambda function. That is 
very good practical design in AWS.

For classification, all the data are divided into three kind of data including public original data, imagery data after processing, user data. The most sensitive 
data is the third one.

\subsubsection{Step 2. High level policy}

Because the user data stored in RDS is the highly sensitive data in this demo, only the Java instances are allowed to visit it. And the entitlement matrix 
is shown as Fig.~\ref{matrix}

\begin{figure}[htbp]
    \centerline{\includegraphics[width=260pt]{images/matrix.png}}
    \caption{Entitlement matrix}
    \label{matrix}
\end{figure}

There are some accurate permission control methods provided by MySQL. The entitlement matrix is made by the MySQL privileges. Admin account is the supper administrator 
which is managed by the project manager role. It is responsible for the management about database creating and auditing. And also, resource based policies provided 
by IAM also give a basic data security, which is the role named AWSServiceRoleForRDS allowing the EC2 instance to visit RDS. At the application layer, the guest role 
have no permission to read the user data. At the data shring layer, the user data has no need to share, so it does not take it into consideration. At the auditing layer, 
project manager is responsible for the daily auditing of the account based auditing.

\subsubsection{Step 3. Encryption}

From the entrance, https is the first consideration of security. Https protocol uses TLS which is a kind of asymmetric encryption, and when the secret key are exchanged, 
it uses symmetric encryption to transfer data. All of the data can be protected by it. Because this demo has no http domain name, https has not configured.

For the data at rest encryption, RDS can enable the encryption when the database is created. And the key is stored in KMS. It is the cloud handles encryption.

For the data in motion encryption, https is the most useful method between users and this demo.

\subsubsection{Step 4. What is more}

Data in this project is not so highly sensitive. For example, S3 data is public for everyone, the calculating data is also public for every authenticated user. Only user 
information do not allow to be public to everyone. The reasonable security is good for the performance for a internet demo. Generally, after the above steps, the data 
security would be sufficient, but the devil is in the detail, every step need to be very careful to implement, and make sure that performance does not degrade too much.

@@

The last step is to configure the security groups for step 1 and 2. In this demo, 3 zones are divided for 3 subnets, which is shown as Fig.~\ref{Security}. The inbound 
rules of zone A and B allows port 80, which is the http service port connected by ELB in front of them. The inbound of zone C allows port 8080, which is the Tomcat 
service port connected by instances in the zone A and B. And the outbound allows port 3306, which is the MySQL service port.

@@

Totally it spend 70\$. The imagery processing accounted for 50 percent. EC2 accounted for 20 percent. RDS accounted for 30 percent.
